Data cleaning for mass mobiliziation data version

### 2024-01-19 Scripts/authoritarian_only.Rmd
Updates to intro

These patterns highlight a puzzle generated by existing research on the relationship between election manipulation and popular protest. The topic has significant implications for authoritarian governance and democratization, and as such has been a very active subject of study. However, the various theoretical perspectives brought to bear on the topic have generated competing predictions. To briefly summarize: for some models, election fraud is a tool of weak incumbents. As a result, incumbents avoid fraud when it might be exposed and reveal their weakness to potential protesters\textemdash an auspicious prediction for democratization and ultimately the under-pinning of 'self-enforcing' democracy [@fearon2011]. For others, fraud is committed by weak and strong incumbents alike, making protest a risky gamble the opposition undertakes for other reasons. In these models, fraud may or may not be deterred based on other exogenous factors: a dubious, though not completely dismissive, prospect for democratization and self-enforcing democracy. Lastly, a third school of thought holds that election fraud is an indicator of genuine incumbent strength. This approach, which is expanded upon below,

Events like those in Belarus are puzzling because many theories of election manipulation expect that incumbents will work hard to avoid them. A large, sustained protest movement creates a moment of heightened risk for the regime; the uncertainty of the outcome creates opportunities for elite defection, splits in the security services, and other negative outcomes.  On some occasions, like Ukraine's Orange Revolution or the People Power Revolution in the Philippines, these protests can result in the fall of an incumbent and a political opening. For this reason, many scholars---especially those working in the formal modeling tradition---have identified the risk that election manipulation will spark protest as a major deterrent to regimes working to engineer election outcomes. Often, though, incumbents can rely on superior resources, elite solidarity, and repressive capacity to quash electoral protests. How threatening, then, are electoral protests really, and can that threat constrain electoral manipulation by governments?

In this paper, I argue that protest risk rarely serves as a deterrent to election manipulation for two reasons. First, election fraud is not only carried out by the weak types assumed in some formal models, but also by strong, cohesive ruling parties. The ambiguity of the electoral environment outside liberal democracies, where political and civil liberties may not be fully protected, makes it difficult for opposition actors to correctly distinguish between the two. As a result, we observe a high proportion of 'failed' protest movements, and\textemdash most likely\textemdash instances where weak governments go un-protested. Second, if electoral protests do materialize, their success or failure quickly becomes untethered from the severity of manipulation itself. Instead, the noisy election-day signal of regime strength is replaced by much clearer signals in the contest with protesters. Consequently, there is little penalty for severe manipulation in terms of protest risk.

Testing this proposition requires looking beyond binary measures of protest, and toward measures of its scope. Research on the risk posed to governments by electoral protest often acknowledges---whether explicitly or implicitly---the importance of broad-based protest campaigns, rather than one-off events [@Bunce2006;@tucker2007;@DAnieri2006;@Carnaghan2016;@bunce2010]. This implicit assumption has largely been overlooked in theories and empirical studies of the relationship between election manipulation and protest, however. In most cases, the risk of protest has both been conceptualized and operationalized as a binary outcome: protests occur or they do not. This approach obscures the importance of the number and size of electoral protests in a ruling party's calculation of the risk involved in manipulation an election.

>>>>

These patterns highlight a puzzle generated by existing research on the relationship between election manipulation and popular protest. The topic has significant implications for authoritarian governance and democratization, and as such has been a very active subject of study. However, the various theoretical perspectives brought to bear on the topic have generated competing predictions. To briefly summarize: for some models, election fraud is a tool of weak incumbents. As a result, incumbents avoid fraud when it might be exposed and reveal their weakness to potential protesters\textemdash an auspicious prediction for democratization and ultimately the under-pinning of 'self-enforcing' democracy [@fearon2011]. For others, fraud is committed by weak and strong incumbents alike, making protest a risky gamble the opposition undertakes for other reasons. In these models, fraud may or may not be deterred based on other exogenous factors: a dubious, though not completely dismissive, prospect for democratization and self-enforcing democracy. Lastly, a third school of thought holds that election fraud is an indicator of genuine incumbent strength. This approach, which is expanded upon below, is a pessimistic account for democracy. If this model is correct, it is authoritarian politics rather than democracy that is self-enforcing\textemdash the ability to commit election fraud helps win elections, signal strength, deter challengers under most conditions, and put down protest movements if they do begin. This paper argues that the third model best fits the overall pattern of the data, and is supported by specific hypothesis tests.

In this paper, I argue that\textemdash in keeping with the idea of 'informational autocracy' (ADD CITES HERE)\textemdash an election outcome produces a signal of the relative strength of the incumbent. As Magaloni (2008) and others have noted, incumbents typically work to produce a higher margin of victory in the election, in order to demonstrate their strength and induce cooperation from other actors in society. In some theories, this only works if the votes for the incumbent are largely 'genuine' (i.e. not fabricated), or produced using the incumbent's organizational resources (i.e. vote-buying and intimidation). (ADD CITES HERE, INCLUDING TO HARVEY AND M). These two kinds of votes correspond to two of the three 'pillars of stability' identified by Gerschewski (2013) (ADD CITE): legitimation and cooptation. Fraud is considered a form of cheap talk in these models, which opposition actors can discount if they become aware of it.

However, these models overlook that engineering widespread fraud requires control over patronage resources and the criminal and judicial apparatus (ADD CITES to HARVEY). As a result, they overlook the fact that high levels of fraud are a sign of incumbent strength in cooptation and Gerschewski's third pillar: repression. Both of these tools can be useful for defusing or dismantling an emergent protest movement. As a result, effective fraudsters should also be effective protest-crushers. This helps explain the broad pattern, where most fraudulent elections go unprotested, and among those that do generate protest, the vast majority fail to dislodge the incumbent. Consequently, there is little penalty for severe manipulation in terms of protest risk, and little deterrent effect.

Testing this proposition in more depth is difficult.  requires looking beyond binary measures of protest, and toward measures of its scope. Research on the risk posed to governments by electoral protest often acknowledges---whether explicitly or implicitly---the importance of broad-based protest campaigns, rather than one-off events [@Bunce2006;@tucker2007;@DAnieri2006;@Carnaghan2016;@bunce2010]. This implicit assumption has largely been overlooked in theories and empirical studies of the relationship between election manipulation and protest, however. In most cases, the risk of protest has both been conceptualized and operationalized as a binary outcome: protests occur or they do not. This approach obscures the importance of the number and size of electoral protests in a ruling party's calculation of the risk involved in manipulation an election.
